Component-Based mruby Platform for IoT Devices

### 2018-02-24 ipsj/reply_letter/paper.tex
Fix to 'highlighted'

We highly appreciate the insightful suggestions and detailed valuable comments on our paper.
The suggestions of the reviewers are very helpful for us and the suggestions are now incorporated in the revised paper as follows.
We have attached the last paper review and revised paper in our reply letter.
In the revised paper, newly added and modified sentences are written in the bold and red colored font so that the reviewers can easily find them.
We hope the editor and the reviewers will be satisfied with our replies to the comments and the revised paper.
\newline\newline

@@

\begin{itembox}[|]{4.2 Performance of TINET+TECS}
\end{itembox}\\

>>>>

We highly appreciate the insightful suggestions and detailed valuable comments on our paper.
The suggestions of the reviewers are very helpful for us and the suggestions are now incorporated in the revised paper as follows.
We have attached the last paper review and revised paper in our reply letter.
In the revised paper, newly added and modified sentences are highlighted so that the reviewers can easily find them.
We hope the editor and the reviewers will be satisfied with our replies to the comments and the revised paper.
\newline\newline

@@

\begin{itembox}[|]{4.2 Performance of TINET+TECS}
    \centering
    {\tabcolsep = 1mm
    \begin{tabular}{c|r|r|r|r}
        \hline\hline
                               &   text       &  data    &   bss      &  total     \\ \hline
        TINET                  &   183.94 KB  &  5.37 KB &  132.03 KB &  322.34 KB \\
        TINET+TECS (TCP)       &   169.48 KB  &  5.37 KB &  149.01 KB &  323.96 KB \\
        TINET+TECS (UDP)       &   169.26 KB  &  5.37 KB &  149.04 KB &  323.77 KB \\
        TINET+TECS (TCP+UDP)   &   170.73 KB  &  5.37 KB &  149.13 KB &  325.23 KB \\
        \hline
        \multicolumn{5}{r}{Including the application and kernel objects}
    \end{tabular}
    }
\end{itembox}\\
